Evolutionary Computing and Machine Learning

### 2018-08-27 AI/EC.tex
8.27

\title{Near-Data Processing}
\author{陈辉}
\date{}
\begin{document}
\maketitle
\tableofcontents
\newpage
\part{文献}
\section{\textit{Evolution-Strategies-as-a-Scalable-Alternative-to-Reinforcement-Learning}}
\paper{Evolution-Strategies-as-a-Scalable-Alternative-to-Reinforcement-Learning}{1}
\section{\textit{NEAR-DATA-PROCESSING-FOR-MACHINE-LEARNING}}
\paper{NEAR-DATA-PROCESSING-FOR-MACHINE-LEARNING}{1}
\section{\textit{Practical-Near-Data-Processing-for-In-memory-Analytics-Frameworks}}
See paper\paper{Practical-Near-Data-Processing-for-In-memory-Analytics-Frameworks}{1}
See presentation\paper{Practical-Near-Data-Processing-for-In-memory-Analytics-Frameworks(Presentation)}{1}

\includepdf[link=true,pages=-,fitpaper]{./papers/Evolution-Strategies-as-a-Scalable-Alternative-to-Reinforcement-Learning.pdf}
\includepdf[link=true,pages=-,fitpaper]{./papers/NEAR-DATA-PROCESSING-FOR-MACHINE-LEARNING.pdf}
\includepdf[link=true,pages=-,fitpaper]{./papers/Practical-Near-Data-Processing-for-In-memory-Analytics-Frameworks.pdf}
\includepdf[link=true,pages=-,fitpaper]{./papers/Practical-Near-Data-Processing-for-In-memory-Analytics-Frameworks(Presentation).pdf}

%\includepdf[link=true,pages=-,fitpaper]{./papers/<++>.pdf}
%\includepdf[link=true,pages=-,fitpaper,angle=-90]{./papers/<++>.pdf}

>>>>

\title{Evolutionary Computing and Machine Learning}
\author{陈辉}
\date{}
\begin{document}
\maketitle
\tableofcontents
\newpage
\part{文献}
\section{\textit{Simple-Evolutionary-Optimization-Can-Rival-Stochastic-Gradient-Descent-in-Neural-Networks}}
\paper{Simple-Evolutionary-Optimization-Can-Rival-Stochastic-Gradient-Descent-in-Neural-Networks}{1}

\includepdf[link=true,pages=-,fitpaper]{./papers/Simple-Evolutionary-Optimization-Can-Rival-Stochastic-Gradient-Descent-in-Neural-Networks.pdf}
%\includepdf[link=true,pages=-,fitpaper]{./papers/<++>.pdf}
%\includepdf[link=true,pages=-,fitpaper,angle=-90]{./papers/<++>.pdf}
